Finding Code Clone Refactoring Techniques by Mapping Clone Context

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{todonotes}
\addbibresource{refs.bib}

@@

\todo[inline]{add more details here, especially about comparison with previous studies.}
\section{Conclusion}
We defined categories to argue about the contextual information of code clones. These categories are:
\begin{itemize}
  \item \textbf{Clone Relation}: The inheritance relation between clone instances in a clone class.
  \item \textbf{Clone Location}: The location of clone instances in the codebase.
  \item \textbf{Clone Contents}: The contents of clone instances in the codebase.
\end{itemize}
For each category we propose subcategories to get more insight into the number of transformations required for the refactoring and their impact on the maintainability of the software. We measure the distribution of clones over these categories on a corpus of 2,267 open-source systems to determine in which contexts most clones are found.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{todonotes}
\addbibresource{refs.bib}
\usepackage{makecell}

@@

Comparing our results for the relation categories to the similar study of Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated}, we get the percentages stated in. They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types. Table \ref{tab:dcra-relation} displays the result of this analysis. We added percentages and ordering to this table for easier comparison with the results of our work (see \ref{sec:relationresults}). We also added the percentages of our work to this table.

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrrr@{}}
\toprule
                         & \makecell{# clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
Same Class               & 5,645  & 32.1\%     & 26.8\%    \\
Same External Superclass & 4,384  & 25.0\%     & 20.6\%   \\
Unrelated Class          & 2,758  & 15.7\%     & 18.4\%    \\
Sibling Class            & 2,721  & 15.5\%     & 18.2\%    \\
Common Hierarchy Class   & 970    & 5.5\%      & 0.8\%    \\
Same Method              & 569    & 3.2\%      & 10.5\%    \\
First Cousin Class       & 416    & 2.4\%      & 1.4\%    \\
Superclass               & 91     & 0.5\%      & 3.1\%    \\
Ancestor Class           & 13     & 0.1\%      & 0.2\%    \\ \bottomrule
\end{tabular}
\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
\label{tab:dcra-relation}
\end{table}

Some of our results differ quite a lot from their results. We think this is mostly accounted due to two differences in their setup:
\begin{itemize}
\item Fontana et al. use a corpus consisting of large higher-quality open-source software systems \cite{tempero2010qualitas} where we use a more varied corpus \cite{githubCorpus2013}.
\item Fontana et al. use clone pairs while we use clone classes.
\end{itemize}

\section{Conclusion}
We defined categories to argue about the contextual information of code clones. These categories are:
\begin{itemize}
  \item \textbf{Clone Relation}: The inheritance relation between clone instances in a clone class.
  \item \textbf{Clone Location}: The location of clone instances in the codebase.
  \item \textbf{Clone Contents}: The contents of clone instances in the codebase.
\end{itemize}
For each category we propose subcategories to get more insight into the number of transformations required for the refactoring and their impact on the maintainability of the software. We measure the distribution of clones over these categories on a corpus of 2,267 open-source systems to determine in which contexts most clones are found.
